Self Referencing Sequences

### 2014-11-06 draft.tex
Edits to Equivalence

This monotonicity is true in general, and we can in fact make a stronger statement on the value of the read distance at a given index.
\begin{lemma} 
\label{readdistformula}
Let $\{a_i\}$ be any self referencing sequence generated by some cycle of positive integers. Then the read distance for the number at index $i>1$, is 
\begin{equation*}
\sum_{k=1}^{i-1}( a_k - 1),
\end{equation*} 
and the read distance for the number at index $1$ is always 0.
\end{lemma}
\begin{proof}
We will prove this using induction. We know that for $i=1$ the read distance is $0$, as the first block always starts at the first number. When $i=2$ the read distance is $a_1-1$. The first block will be of length $a_1$ since the sequence is self referencing, therefore the second block will begin at position $a_1$. The number of elements between position $a_1$ and $2$ is exactly $a_1 -1$.

Now if we assume that our result holds for $i=l$ we would like to show that it holds for $i=l+1$. We know that the distance between the start of the $l$th block and position $l$ is 
\begin{equation*}
\sum_{k=1}^{l-1}( a_k - 1).
\end{equation*} 
This $l$th block has length $a_l$ and so the $l+1$th block will begin $a_l$ positions to the right of the beginning of the $l$th block. Also note that $a_{l+1}$ is one position to the right of $a_l$. Therefore the beginning of the $(l+1)$th block is 
\begin{equation*}
a_l-1 + \sum_{k=1}^{l-1} (a_k-1) = \sum_{k=1}^{l} (a_k-1)
\end{equation*} 
positions to the right of $a_{l+1}$. But this is exactly the reading distance for $a_{l+1}$ and so we have our result.
\end{proof}
Note that because $\{a_i\}$ is generated by positive integers we always have $a_k-1\geq 0$ and so the read distance is monotonically increasing.

@@

Now that we have a nice expression for the value of the read distance at a particular index we can show our first major result which allows us to check only finitely many indices in order to establish that two sequences are equivalent. 
\begin{theorem} 
\label{equivsuff}
Let $\{a_i\}, \{b_i\}$ be two self-referencing sequences generated by the same cycle.If there are integers $m,l$ such that the read distance for $a_m$ and $b_l$ are both $d$ and 
\begin{equation*}
a_{m+k} = b_{l+k},
\end{equation*}
for all $0 \leq k \leq d-1$ then $\{a_i\}$ and $\{b_i\}$ are equivalent. 
\end{theorem}

@@

We also can demonstrate a sufficient condition for equivalence. 
\begin{theorem}
\label{thm:readfirst}
If two sequences are equivalent then the first element of the shared sequence must have the same read distance in both sequences.
\end{theorem}

@@

\begin{corollary}
If two self-referencing sequences are equivalent, then their read distance of the shared subsequence is the same everywhere.
\end{corollary}

@@

\begin{conj} If two sequences $\{a_i\}$ and $\{b_i\}$ are equivalent, then whenever two elements have the same read distances, the two elements are equal. 
\end{conj}

>>>>

This monotonicity is true in general, and we can in fact make a stronger statement on the value of the read distance at a given index.
\begin{lemma} 
\label{readdistformula}
Let $\{a_i\}$ be any self referencing sequence generated by some cycle of positive integers. Then the read distance for the number at index $i>1$, is 
\begin{equation*}
\sum_{k=1}^{i-1}( a_k - 1).
\end{equation*} 
The read distance for the number at index $1$ is always 0.
\end{lemma}
\begin{proof}
We will prove this using induction. We know that for $i=1$ the read distance is $0$, as the first block always starts at the first number. When $i=2$ the read distance is $a_1-1$. The first block will be of length $a_1$ since the sequence is self referencing, therefore the second block will begin at position $a_1$. The number of elements between position $a_1$ and $2$ is exactly $a_1 -1$.

Now if we assume that our result holds for $i=l$ we would like to show that it holds for $i=l+1$. We know that the distance between the start of the $l$th block and position $l$ is 
\begin{equation*}
\sum_{k=1}^{l-1}( a_k - 1).
\end{equation*} 
This $l$th block has length $a_l$ and so the $(l+1)$th block will begin $a_l$ positions to the right of the beginning of the $l$th block.  Additionally $a_{l+1}$ is one position to the right of $a_l$. Therefore the beginning of the $(l+1)$th block is 
\begin{equation*}
(a_l-1 )+ \sum_{k=1}^{l-1} (a_k-1) = \sum_{k=1}^{l} (a_k-1)
\end{equation*} 
positions to the right of $a_{l+1}$. But this is exactly the desired read distance for $a_{l+1}$ and so we have our result.
\end{proof}
Note that because $\{a_i\}$ is generated by positive integers we always have $a_k-1\geq 0$ and so read distance is increases monotonically.

@@

Now that we have a nice expression for the value of the read distance at a particular index we can show our first major result. It will allow us to check only finitely many indices in order to establish that two sequences are equivalent. 
\begin{theorem} 
\label{equivsuff}
Let $\{a_i\}, \{b_i\}$ be two self-referencing sequences generated by the same cycle. If there are integers $m,l$ such that the read distance for $a_m$ and $b_l$ are both $d$ and 
\begin{equation*}
a_{m+k} = b_{l+k},
\end{equation*}
for all $0 \leq k \leq d-1$, then $\{a_i\}$ and $\{b_i\}$ are equivalent. 
\end{theorem}

@@

We can also demonstrate a sufficient condition for equivalence. 
\begin{theorem}
\label{thm:readfirst}
If two sequences are equivalent then the first element of the shared sequence must have the same read distance in both sequences.
\end{theorem}

@@

\begin{corollary}
If two self-referencing sequences are equivalent, then the read distance of their shared subsequence is the same everywhere.
\end{corollary}

@@

\begin{conj} If two sequences $\{a_i\}$ and $\{b_i\}$ are equivalent, then whenever two elements have the same read distances, other than for $i=0$,  the two elements are equal. 
\end{conj}
